
---
title: "MT5000 Data Analytics & Visualisation: Assignment 2 "
format: html
execute:
 echo: false
 warning: false
 message: false
---

## Yellow Fever Vaccination Rate

Meaning of the indicator - Percentage of newborns who survived and who had received the yellow fever vaccination (for at-risk nations where the vaccine is on the national schedule).

Numerator - Number of surviving infants who obtained a dose of the yellow fever vaccination.

Denominator - Total number of infants that have survived

More Information - Only applicable to nations where YF is a danger and YF vaccination is included in the national schedule

Aggregate technique - Population weighted average

## Brief Description

The four figures on this page highlight the status of Yellow fever vaccination among surviving infants in South America and Africa. 

Figure 1 illustrates that the average rate of yellow fever vaccination among infants has increased substantially over the years.

Figure 2 displays the vaccination rate in 2021: the latest year for which data is available. 

Figure 3 outlines the relationship between Yellow fever vaccination rate and life expectancy at birth.

Figure 4 shows the percentage of GDP utilised for military expenditure for the countries surveyed. Countries with high military expenditure are often seen to allocate lower amounts towards Health. 

```{r}
#| include: false
install.packages('tidyverse')
```

```{r}
#| echo: false
library(tidyverse)
```

```{r}
#| echo: false
uni_ind <- read.csv("unicef_indicator_1.csv")
uni_met <- read.csv("unicef_metadata.csv")
```


```{r}
#| echo: false
table_1 <- uni_ind %>%
select(country, year, observation_value)

table_2 <- uni_met
```

```{r}
#| echo: false
table_left_joined <- left_join(table_1, table_2, by = c("country", "year"))
```







```{r}
#| echo: false
data_by_year <- group_by(table_left_joined, year)
```

```{r}
#| echo: false
average_vaccination_per_year <- summarise(data_by_year, mean_observation_value = mean(observation_value))
```


```{r}
#| echo: false
ggplot(data = average_vaccination_per_year) +
aes(x = year, y = mean_observation_value) +
geom_line() +
guides(color ="none")                                         
```


```{r}
#| echo: false
install.packages("maps")
```

```{r}
#| echo: false
library(maps)
```


```{r}
#| echo: false
observation_value_2021 <- table_left_joined %>%
filter(year == 2021)
map_world <- map_data("world")
map_observation_value_2021 <- full_join(map_world, observation_value_2021, by = c("region" = "country"))
ggplot(data = map_observation_value_2021) +
aes(x = long, y = lat, group = group, fill = observation_value) +
geom_polygon() +
scale_fill_gradient(low = "red", high = "green", na.value = "grey") +
labs(
title = "Yellow Fever vaccination rate in 2021",
subtitle = "Data is not available for countries in grey.",
caption = "Source: UNICEF",
x = "Longitude",
y = "Latitude",
fill = "Vaccination Rate"
) +
theme_bw()
```


```{r}
#| echo: false
data_2020 <- filter(table_left_joined, year == "2020")
```



```{r}
#| echo: false
ggplot(data = data_2020) +
aes(x = observation_value, y = Life_expectancy_birth, color= country) +
geom_point() +
geom_smooth(method=lm)
```



```{r}
#| echo: false
data_2021 <- filter(table_left_joined, year == "2021")
```


```{r}
#| echo: false
ggplot(data_2021) +
  aes(x = country, y = Military_expenditure_Percent_GDP) +
  geom_col()
```
                                         
Created by Vijay K Varghese



